### 2019-07-11 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Typo

\textbf{\textcolor{red}{Warning}:}
%
We highlight that \emph{this result is finite-time} and not asymptotic, but if it uses the notation $\textcolor{red}{\underline{\cO}\left(\sqrt{\ln(T)}\right)}$ for simplicity.
This last term $\underline{\cO}\left(\dots)$ does not mean the whole inequality is only valid for $T\to\infty$, but it rather means that at finite time, the inequality is valid with the last term being a function $g(T)$, which is upper-bounded by a certain $c_0 \times \sqrt{\ln(T)}$, from a certain time $T_0$ (\ie, $\forall T \geq T_0$).
It is also the case of the next Theorem~\ref{thm:6:mainRegretBound}.

>>>>

\textbf{\textcolor{red}{Warning}:}
%
We highlight that \emph{this result is finite-time} and not asymptotic, but if it uses the notation $\textcolor{red}{\underline{\cO}\left(\sqrt{\ln(T)}\right)}$ for simplicity.
This last term $\underline{\cO}\left(\dots\right)$ does not mean the whole inequality is only valid for $T\to\infty$, but it rather means that at finite time, the inequality is valid with the last term being a function $g(T)$, which is upper-bounded by a certain $c_0 \times \sqrt{\ln(T)}$, from a certain time $T_0$ (\ie, $\forall T \geq T_0$).
It is also the case of the next Theorem~\ref{thm:6:mainRegretBound}.
